\large
\begin{enumerate}
\item The canteen has two community fridges and a freezer, which may be used by anyone.  All food must be marked with the name of the owner, and the date. Any items which are not labelled, and which have gone off \textit{will} be thrown out. The buffet fridge may \textit{not} be used for storage.
\item We do not charge you for the bottle deposit on beverages purchased in the canteen. Please return your empties, otherwise we lose money. Place the empties in the designated recycling bins in the canteen. 
\item The kitchen is open for anyone to use, as long as you clean up after your self. If you are cooking for many people, please ask the canteen board for permission in advance, in order to avoid scheduling conflicts.
\item Be courteous to the others in the canteen. Please keep the noise down during working hours (8am to 5pm).
\item Clean up after yourself. Cardboard that hasn't been in direct contact with food should be thrown out in the carboard recycling container. Glass with no bottle deposit should be deposited in the glass bin under the sink in the kitchen.
\item Remember to wash up any items you use, and put the items away after use. If you take crockery/cutlery out of the canteen, then you are implicitly promising to return them again.
\item If a KEN tray is full, put it in KEN and start him. Empty him if he is full and put the clean items away.
\item Remember to brew more coffee if you take the last cup -- but please don't brew 5 litres if you are the last person left in the canteen in the evening!
\item Please don't leave food on the cookers/in the ovens to cool down. The table next to the cooker can be used for this purpose.
\item Please don't leave the canteen while making food, as this can be a fire hazard.
\item Taking food from the buffet, fridges, vending machines etc. without payment will be considered as theft and reported to the relevant authorities.
\end{enumerate}
